Titeltext

### 2018-07-26 thesis/paper/paper.tex
Added mandatory qualifier

>>>>

\subsection{Mandatory qualifier (Q21510856)}
The mandatory qualifier constraint requires that a constrained statement has a qualifier with a specific property.

\begin{table}[H]
\caption{Mandatory qualifier constraint (Q21510856)}
\begin{tabularx}{\textwidth}{ ll X}
\hline
Requirement & qualifier on constrained statement \\
\hline
Qualifiers & \makecell{required property (P2306) -- 1 \\ qualifier that the statement must have} \\
\hline
Violation & \makecell{constrained statement without a qualifier with the required property} \\
\hline
Dependency & constrained statement and its qualifiers \\
\hline
Rule features & negation \\
\hline
\end{tabularx}
\end{table}

To find violations of this constraint one would find a tripleEDB with the constrained property, but where no qualifierEDB for the statement and with the required property exists.
